---
title: "R Notebook"
output: html_notebook
---

```{r}
library(tidyverse)
wine = read.csv("~/dataScience/wine.csv")
ggplot(data = wine) + geom_point(mapping = aes(x = AGST, y = Price))
ggplot(data = wine) + geom_point(mapping = aes(x = HarvestRain, y = Price))


x = lm(Price ~ HarvestRain + AGST + WinterRain + Age + FrancePop, data = wine)
summary(x)

x = lm(Price ~ ., data = wine)
summary(x)
```
Let's see price vs AGST & HarvestRain
```{r}
ggplot(data = wine) + 
  geom_point(mapping = aes(x = AGST, y = HarvestRain, color = Price))
```
### Linear Regression

Searching for Price = a + b * AGST
```{r}
lm(Price ~ AGST, data = wine)
```
So the equation is -3.4178 + 0.6351 * AGST
```{r}
ggplot(data = wine) + geom_point(mapping = aes(x = AGST, y = Price, color = Price)) + 
  geom_abline(intercept = -3.4178, slope = 0.6351, color = "blue")
reg = lm(Price ~ AGST, data = wine)
summary(reg)
#step(x)
```

$$ SSE = \sum (\hat{y_i}, y_i)^2 $$
$$ \frac{SSE_1}{SSE_2} <1 \implies model_1 better, >1 \implies model2 better $$
$$ SSE_2 = \sum (\hat{y_i}, \bar{y})^2 = SST = variance $$
$$ \frac{SSE}{SST} $$
$$ R^2 = 1 - \frac{SSE}{SST} $$
How well my model fits the data

```{r}
SSE = sum((reg$residuals)^2)
SSE
SST = sum((wine$Price - mean(wine$Price))^2)
SST
R2 = 1 - SSE/SST
R2
reg = lm(Price ~ AGST + HarvestRain, data = wine)
summary(reg)
```

P(100 Heads) = $$2^{-100}$$
$$ y_i = a + bx + \epsilon_i $$
each line i draw is a random event (supposing multiple datasets of the same kind)
how likely it is that what i see is just a chance
if the true slope was 0 what is the prob that the points are alligned to a slope of, for example, 0.3?
if the prob is < 5% we should be fine

$$ Price = 0.6808 \cdot AGST -0.00457 * HarvestRain $$
```{r}
reg = lm(Price ~ HarvestRain + AGST + WinterRain + Age, data = wine)
summary(reg)
```

