---
title: "Final Project: House Prices: Advanced Regression Techniques"
output: html_notebook
---

Project found on the [Kaggle Site](https://www.kaggle.com/c/house-prices-advanced-regression-techniques).

## Loading Libs and Data
```{r}
install.packages("tidyverse")
install.packages("ggthemes", dependencies = T)
install.packages("reshape2", dependencies = T)
install.packages("Matrix", dependencies = T)
install.packages("xgboost", dependencies = T)
install.packages("Metrics", dependencies = T)
install.packages("randomForest", dependencies = T)
install.packages("dplyr", dependencies = T)
install.packages("caret", dependencies = T)
install.packages("scales", dependencies = T)
install.packages("e1071", dependencies = T)
install.packages("corrplot", dependencies = T)
install.packages("glmnet", dependencies = T)
install.packages("rpart", dependencies = T)
install.packages("repr", dependencies = T)
install.packages("Amelia", dependencies = T)
install.packages("mice", dependencies = T)
install.packages("VIM", dependencies = T)
install.packages("DescTools", dependencies = T)
```


Loading Libs
```{r}
library(tidyverse)
library(ggthemes)
library(rpart)
library(reshape2)
library(Amelia)
library(mice)
library(VIM)
library(ggplot2) # for data visualization
library(stringr) #extracting string patterns
library(Matrix) # matrix transformations
library(glmnet) # ridge, lasso & elastinet
library(xgboost) # gbm
library(randomForest)
library(Metrics) # rmse
library(dplyr) # load this in last so plyr doens't overlap it
library(caret) # one hot encoding
library(scales) # plotting $$
library(e1071) # skewness
library(corrplot) # correlation plot
library(repr)
library(DescTools)
```


Loading the data
```{r}
test <- read.csv("~/dataScience/final/test.csv", stringsAsFactors = F)
train <- read.csv("~/dataScience/final/train.csv", stringsAsFactors = F)
df <- rbind(train[,!(names(train) %in% c("SalePrice"))],test)
house_price_num<-train[, sapply(train, is.numeric)]
house_price_cat<-train[, sapply(train, is.factor)]
```


## Tidying Data

First plot: SquareFeet vs Sale Price
```{r}
ggplot(train) +  geom_point(aes(x = GrLivArea, y = SalePrice)) + theme_minimal()

# Check for outliers on living area
ggplot(train, aes(GrLivArea)) +
  geom_histogram(fill = 'light green', color = 'black') +
  theme_minimal()
```

We can see that there are four outliers, let's remove them:
TODO: DO THIS AFTER!!
```{r}
##train <- train[-which(train$GrLivArea > 4000),] #why is there a comma?
train <- train[-which(train$GrLivArea > 4000),]
# No more outliers
ggplot(train) +  geom_point(aes(x = GrLivArea, y = SalePrice)) + theme_minimal()
```

We need to handle NA in our data
```{r}
missmap(train[,1:80],
        main = "Missing values in Housing Prices Dataset",
        y.labels = NULL,
        y.at = NULL)

# List of NAs
sort(colSums(sapply(train, is.na)), decreasing = T)

cMiss = function(x){sum(is.na(x))}
CM <- sort(apply(train,2,cMiss),decreasing=T)
barplot(CM[CM!=0],
        las=2,
        cex.names=0.6,
        ylab="Count",
        ylim=c(0,3000),
        horiz=F,
        col="#AFC0CB",
        main=paste(toString(sum(CM!=0)), "variables with missing values in dataset"))
```

Now we need to substitute NAs with values
https://www.kaggle.com/clustersrus/house-prices-dealing-with-the-missing-data
https://www.kaggle.com/bisaria/handling-missing-data/notebook
```{r}
# PoolQC: if NA -> No Pool
train$PoolQC[is.na(train$PoolQC)] <- "NoPool"

# MiscFeature: if NA -> None
train$MiscFeature[is.na(train$MiscFeature)] <- "None"

# Alley: if NA -> No Alley Access
train$Alley[is.na(train$Alley)] <- "NoAlleyAccess"

# Fence: if NA -> No Fence
train$Fence[is.na(train$Fence)] <- "NoFence"

# FireplaceQu: If NA -> No FirePlace
train$FireplaceQu[is.na(train$FireplaceQu)] <- "NoFirePlace"

# Garage: No area -> No Garage, as simple as that
train$GarageYrBlt[train$GarageArea %in% c(0,NA) & is.na(train$GarageYrBlt)] <- "NoGarage"
train$GarageFinish[train$GarageArea %in% c(0,NA) & is.na(train$GarageFinish)] <- "NoGarage"
train$GarageQual[train$GarageArea %in% c(0,NA) & is.na(train$GarageQual)] <- "NoGarage"
train$GarageCond[train$GarageArea %in% c(0,NA) & is.na(train$GarageCond)] <- "NoGarage"
train$GarageType[train$GarageArea %in% c(0,NA) & is.na(train$GarageType)] <- "NoGarage"
# Garage: If the area is 0 there can be no size for cars, reverse apply too. (look description)
train$GarageCars[train$GarageArea %in% c(0,NA) & is.na(train$GarageCars)] <- 0 
train$GarageArea[train$GarageCars %in% c(0,NA) & is.na(train$GarageArea)] <- 0

# Basement: for starters, if the squarefeet is 0/NA we can't have a basement
train$BsmtFullBath[train$TotalBsmtSF %in% c(0,NA) & is.na(train$BsmtFullBath)] <- 0
train$BsmtHalfBath[train$TotalBsmtSF %in% c(0,NA) & is.na(train$BsmtHalfBath)] <- 0
train$BsmtFinSF1[train$TotalBsmtSF %in% c(0,NA) & is.na(train$BsmtFinSF1)] <- 0
train$BsmtFinSF2[train$TotalBsmtSF %in% c(0,NA) & is.na(train$BsmtFinSF2)] <- 0
train$BsmtUnfSF[train$TotalBsmtSF %in% c(0,NA) & is.na(train$BsmtUnfSF)] <- 0
train$TotalBsmtSF[train$TotalBsmtSF %in% c(0,NA) & is.na(train$TotalBsmtSF)] <- 0
train$BsmtQual[train$TotalBsmtSF %in% c(0,NA) & is.na(train$BsmtQual)] <- "NoBasement"
train$BsmtFinType1[train$TotalBsmtSF %in% c(0,NA) & is.na(train$BsmtFinType1)] <- "NoBasement"
train$BsmtFinType2[train$TotalBsmtSF %in% c(0,NA) & is.na(train$BsmtFinType2)] <- "NoBasement"
train$BsmtExposure[train$TotalBsmtSF %in% c(0,NA) & is.na(train$BsmtExposure)] <- "NoBasement"
train$BsmtCond[train$TotalBsmtSF %in% c(0,NA) & is.na(train$BsmtCond)] <- "NoBasement"

sort(colSums(sapply(train, is.na)), decreasing = T)

CM <- sort(apply(train,2,cMiss),decreasing=T);
barplot(CM[CM != 0], las = 2, cex.names = 0.6, ylab = "Count", ylim = c(0, 500), horiz = F,  col = "#AFC0CB", main =  paste(toString(sum(CM != 0)), "variables with missing values in dataset"))
```
```{r}
# PoolQC: if NA -> No Pool
test$PoolQC[is.na(test$PoolQC)] <- "NoPool"

# MiscFeature: if NA -> None
test$MiscFeature[is.na(test$MiscFeature)] <- "None"

# Alley: if NA -> No Alley Access
test$Alley[is.na(test$Alley)] <- "NoAlleyAccess"

# Fence: if NA -> No Fence
test$Fence[is.na(test$Fence)] <- "NoFence"

# FireplaceQu: If NA -> No FirePlace
test$FireplaceQu[is.na(test$FireplaceQu)] <- "NoFirePlace"

# Garage: No area -> No Garage, as simple as that
test$GarageYrBlt[test$GarageArea %in% c(0,NA) & is.na(test$GarageYrBlt)] <- "NoGarage"
test$GarageFinish[test$GarageArea %in% c(0,NA) & is.na(test$GarageFinish)] <- "NoGarage"
test$GarageQual[test$GarageArea %in% c(0,NA) & is.na(test$GarageQual)] <- "NoGarage"
test$GarageCond[test$GarageArea %in% c(0,NA) & is.na(test$GarageCond)] <- "NoGarage"
test$GarageType[test$GarageArea %in% c(0,NA) & is.na(test$GarageType)] <- "NoGarage"
# Garage: If the area is 0 there can be no size for cars, reverse apply too. (look description)
test$GarageCars[test$GarageArea %in% c(0,NA) & is.na(test$GarageCars)] <- 0 
test$GarageArea[test$GarageCars %in% c(0,NA) & is.na(test$GarageArea)] <- 0

# Basement: for starters, if the squarefeet is 0/NA we can't have a basement
test$BsmtFullBath[test$TotalBsmtSF %in% c(0,NA) & is.na(test$BsmtFullBath)] <- 0
test$BsmtHalfBath[test$TotalBsmtSF %in% c(0,NA) & is.na(test$BsmtHalfBath)] <- 0
test$BsmtFinSF1[test$TotalBsmtSF %in% c(0,NA) & is.na(test$BsmtFinSF1)] <- 0
test$BsmtFinSF2[test$TotalBsmtSF %in% c(0,NA) & is.na(test$BsmtFinSF2)] <- 0
test$BsmtUnfSF[test$TotalBsmtSF %in% c(0,NA) & is.na(test$BsmtUnfSF)] <- 0
test$TotalBsmtSF[test$TotalBsmtSF %in% c(0,NA) & is.na(test$TotalBsmtSF)] <- 0
test$BsmtQual[test$TotalBsmtSF %in% c(0,NA) & is.na(test$BsmtQual)] <- "NoBasement"
test$BsmtFinType1[test$TotalBsmtSF %in% c(0,NA) & is.na(test$BsmtFinType1)] <- "NoBasement"
test$BsmtFinType2[test$TotalBsmtSF %in% c(0,NA) & is.na(test$BsmtFinType2)] <- "NoBasement"
test$BsmtExposure[test$TotalBsmtSF %in% c(0,NA) & is.na(test$BsmtExposure)] <- "NoBasement"
test$BsmtCond[test$TotalBsmtSF %in% c(0,NA) & is.na(test$BsmtCond)] <- "NoBasement"

sort(colSums(sapply(test, is.na)), decreasing = T)

CM <- sort(apply(test,2,cMiss),decreasing=T);
barplot(CM[CM != 0], las = 2, cex.names = 0.6, ylab = "Count", ylim = c(0, 500), horiz = F,  col = "#AFC0CB", main =  paste(toString(sum(CM != 0)), "variables with missing values in dataset"))
```


We took care of most of the data, let's see how to deal with the remaining:
```{r}
# Handle MasVnrType and Area
#table(train$MasVnrType, useNA = "ifany")
#table(train$MasVnrArea, useNA = "ifany")
# We will use the mode for type and area
train$MasVnrType[is.na(train$MasVnrType)] <- "None"
train$MasVnrArea[is.na(train$MasVnrArea)] <- 0

# Handle MSZoning
table(train$MSZoning, useNA = "ifany")
# We will take the mode (most frequent) for all NA
train$MSZoning[is.na(train$MSZoning)] <- "RL"

# Basement
MissBsmt = c('BsmtCond','BsmtExposure','BsmtQual','BsmtFinType2')
train[!complete.cases(train[,names(train) %in% MissBsmt]),names(train) %in% names(train)[which(grepl("Bsmt",names(train)))]]
# All basements with Exposure = NA are unfinished
table(train$BsmtExposure, useNA = "ifany")
train$BsmtExposure[is.na(train$BsmtExposure)] <- "No"
# ALQ closest val to median
train$BsmtFinType2[is.na(train$BsmtFinType2)] <- "ALQ"
# BsmtQual is dependant to house style (TODO: why tho?) give the mode of bsmtQual based on housestyle
train$HouseStyle[is.na(train$BsmtQual)]
table(train$BsmtQual, useNA = "ifany")
train$BsmtQual[is.na(train$BsmtQual) & train$HouseStyle == "2Story"] <- "Gd"
train$BsmtQual[is.na(train$BsmtQual) & train$HouseStyle == "1.5Fin"] <- "TA"
# BsmtCond
(TableBsmtCond <- table(train$HouseStyle, train$BsmtCond))
# We can give them TA since is the mode
train$BsmtCond[is.na(train$BsmtCond)] <- "TA"

# Utilities: Mode
table(train$Utilities, useNA = "ifany")
train$Utilities[is.na(train$Utilities) ] <- "AllPub"

# Functional
table(train$Functional, useNA = "ifany")
train$Functional[is.na(train$Functional) ] <- "Typ"

# Exterior1: Predict with rpart
table(train$Exterior1st, useNA = "ifany")
# Likely predictors
col.pred <- c("BldgType", "HouseStyle", "OverallQual", "OverallCond", "YearBuilt", "YearRemodAdd", "RoofStyle", "RoofMatl", "Exterior1st", "Exterior2nd", "MasVnrType", "MasVnrArea", "ExterQual", "ExterCond")
# Predict Exterior1st
ext1.rpart <- rpart(
  as.factor(Exterior1st) ~ .,
  data = train[!is.na(train$Exterior1st), col.pred],
  method = "class",
  na.action = na.omit
  )
train$Exterior1st[is.na(train$Exterior1st)] <- as.character(predict(ext1.rpart, train[is.na(train$Exterior1st),col.pred], type = "class"))

# Exterior2: Predict with rpart
table(train$Exterior2nd, useNA = "ifany")
ext2.rpart <- rpart(
  as.factor(Exterior2nd) ~ .,
  data = train[!is.na(train$Exterior2nd), col.pred],
  method = "class",
  na.action = na.omit
  )
train$Exterior2nd[is.na(train$Exterior2nd)] <- as.character(predict(ext2.rpart, train[is.na(train$Exterior2nd),col.pred], type = "class"))

# Electrical: mode
table(train$Electrical, useNA = "ifany")
train$Electrical[is.na(train$Electrical) ] <- "SBrkr"

# KitchenQual: Rpart
table(train$KitchenQual, useNA = "ifany")
col.pred <- c("BldgType", "HouseStyle", "OverallQual", "OverallCond", "YearBuilt", "YearRemodAdd", "KitchenQual")
kit.rpart <- rpart(
  as.factor(KitchenQual) ~ .,
  data = train[!is.na(train$KitchenQual), col.pred],
  method = "class",
  na.action = na.omit
  )
train$KitchenQual[is.na(train$KitchenQual)] <- as.character(predict(kit.rpart, train[is.na(train$KitchenQual),col.pred], type = "class"))

# SaleType: mode
table(train$SaleType, useNA = "ifany")
train$SaleType[is.na(train$SaleType) ] <- "WD"

# GarageYrBlt: rpart
table(train$GarageYrBlt, useNA = "ifany")
col.pred <- c("GarageType", "GarageYrBlt", "GarageFinish", "GarageQual","GarageCond","YearBuilt", "GarageCars", "GarageArea")
blt.rpart <- rpart(
  as.factor(GarageYrBlt) ~ .,
  data = train[!is.na(train$GarageYrBlt), col.pred],
  method = "class",
  na.action = na.omit
  )
train$GarageYrBlt[is.na(train$GarageYrBlt)] <- as.numeric(as.character(predict(blt.rpart, train[is.na(train$GarageYrBlt),col.pred], type = "class")))

# GarageQual: mode
table(train$GarageQual, useNA = "ifany")
train$GarageQual[is.na(train$GarageQual) ] <- "TA"

# GarageCond: mode
table(train$GarageCond, useNA = "ifany")
train$GarageCond[is.na(train$GarageCond) ] <- "TA"

# GarageFinish: unfinished
table(train$GarageFinish, useNA = "ifany")
train$GarageFinish[is.na(train$GarageFinish)] <- "Unf"

CM <- sort(apply(train,2,cMiss),decreasing=T);
barplot(CM[CM != 0], las = 2, cex.names = 0.6, ylab = "Count", ylim = c(0, 500), horiz = F,  col = "#AFC0CB", main =  paste(toString(sum(CM != 0)), "variables with missing values in dataset"))
```

```{r}
# Handle MasVnrType and Area
#table(test$MasVnrType, useNA = "ifany")
#table(test$MasVnrArea, useNA = "ifany")
# We will use the mode for type and area
test$MasVnrType[is.na(test$MasVnrType)] <- "None"
test$MasVnrArea[is.na(test$MasVnrArea)] <- 0

# Handle MSZoning
table(test$MSZoning, useNA = "ifany")
# We will take the mode (most frequent) for all NA
test$MSZoning[is.na(test$MSZoning)] <- "RL"

# Basement
MissBsmt = c('BsmtCond','BsmtExposure','BsmtQual','BsmtFinType2')
test[!complete.cases(test[,names(test) %in% MissBsmt]),names(test) %in% names(test)[which(grepl("Bsmt",names(test)))]]
# All basements with Exposure = NA are unfinished
table(test$BsmtExposure, useNA = "ifany")
test$BsmtExposure[is.na(test$BsmtExposure)] <- "No"
# ALQ closest val to median
test$BsmtFinType2[is.na(test$BsmtFinType2)] <- "ALQ"
# BsmtQual is dependant to house style (TODO: why tho?) give the mode of bsmtQual based on housestyle
test$HouseStyle[is.na(test$BsmtQual)]
table(test$BsmtQual, useNA = "ifany")
test$BsmtQual[is.na(test$BsmtQual) & test$HouseStyle == "2Story"] <- "Gd"
test$BsmtQual[is.na(test$BsmtQual) & test$HouseStyle == "1.5Fin"] <- "TA"
# BsmtCond
(TableBsmtCond <- table(test$HouseStyle, test$BsmtCond))
# We can give them TA since is the mode
test$BsmtCond[is.na(test$BsmtCond)] <- "TA"

# Utilities: Mode
table(test$Utilities, useNA = "ifany")
test$Utilities[is.na(test$Utilities) ] <- "AllPub"

# Functional
table(test$Functional, useNA = "ifany")
test$Functional[is.na(test$Functional) ] <- "Typ"

# Exterior1: Predict with rpart
table(test$Exterior1st, useNA = "ifany")
# Likely predictors
col.pred <- c("BldgType", "HouseStyle", "OverallQual", "OverallCond", "YearBuilt", "YearRemodAdd", "RoofStyle", "RoofMatl", "Exterior1st", "Exterior2nd", "MasVnrType", "MasVnrArea", "ExterQual", "ExterCond")
# Predict Exterior1st
ext1.rpart <- rpart(
  as.factor(Exterior1st) ~ .,
  data = test[!is.na(test$Exterior1st), col.pred],
  method = "class",
  na.action = na.omit
  )
test$Exterior1st[is.na(test$Exterior1st)] <- as.character(predict(ext1.rpart, test[is.na(test$Exterior1st),col.pred], type = "class"))

# Exterior2: Predict with rpart
table(test$Exterior2nd, useNA = "ifany")
ext2.rpart <- rpart(
  as.factor(Exterior2nd) ~ .,
  data = test[!is.na(test$Exterior2nd), col.pred],
  method = "class",
  na.action = na.omit
  )
test$Exterior2nd[is.na(test$Exterior2nd)] <- as.character(predict(ext2.rpart, test[is.na(test$Exterior2nd),col.pred], type = "class"))

# Electrical: mode
table(test$Electrical, useNA = "ifany")
test$Electrical[is.na(test$Electrical) ] <- "SBrkr"

# KitchenQual: Rpart
table(test$KitchenQual, useNA = "ifany")
col.pred <- c("BldgType", "HouseStyle", "OverallQual", "OverallCond", "YearBuilt", "YearRemodAdd", "KitchenQual")
kit.rpart <- rpart(
  as.factor(KitchenQual) ~ .,
  data = test[!is.na(test$KitchenQual), col.pred],
  method = "class",
  na.action = na.omit
  )
test$KitchenQual[is.na(test$KitchenQual)] <- as.character(predict(kit.rpart, test[is.na(test$KitchenQual),col.pred], type = "class"))

# SaleType: mode
table(test$SaleType, useNA = "ifany")
test$SaleType[is.na(test$SaleType) ] <- "WD"

# GarageYrBlt: rpart
table(test$GarageYrBlt, useNA = "ifany")
col.pred <- c("GarageType", "GarageYrBlt", "GarageFinish", "GarageQual","GarageCond","YearBuilt", "GarageCars", "GarageArea")
blt.rpart <- rpart(
  as.factor(GarageYrBlt) ~ .,
  data = test[!is.na(test$GarageYrBlt), col.pred],
  method = "class",
  na.action = na.omit
  )
test$GarageYrBlt[is.na(test$GarageYrBlt)] <- as.numeric(as.character(predict(blt.rpart, test[is.na(test$GarageYrBlt),col.pred], type = "class")))

# GarageQual: mode
table(test$GarageQual, useNA = "ifany")
test$GarageQual[is.na(test$GarageQual) ] <- "TA"

# GarageCond: mode
table(test$GarageCond, useNA = "ifany")
test$GarageCond[is.na(test$GarageCond) ] <- "TA"

# GarageFinish: unfinished
table(test$GarageFinish, useNA = "ifany")
test$GarageFinish[is.na(test$GarageFinish)] <- "Unf"

CM <- sort(apply(test,2,cMiss),decreasing=T);
barplot(CM[CM != 0], las = 2, cex.names = 0.6, ylab = "Count", ylim = c(0, 500), horiz = F,  col = "#AFC0CB", main =  paste(toString(sum(CM != 0)), "variables with missing values in dataset"))
```


Let's handle LotFrontage
```{r}
table(train$LotFrontage, useNA = "ifany")

# Likely predictors
col.pred <- c("MSSubClass", "MSZoning", "LotFrontage", "LotArea", "Street", "Alley", "LotShape", "LandContour", "LotConfig", "LandSlope", "BldgType", "HouseStyle", "YrSold", "SaleType", "SaleCondition")

# Predict LotFrontage
frntage.rpart <- rpart(
  LotFrontage ~ .,
  data = train[!is.na(train$LotFrontage), col.pred],
  method = "anova",
  na.action = na.omit
  )

# Let us plot the existing and imputed values and check if imputed values follow the same patten
train.frontage <-
  as.data.frame(rbind(cbind(rep(
  "Existing", nrow(train[!is.na(train$LotFrontage), ])
  ), train[!is.na(train$LotFrontage), "LotFrontage"]),
  cbind(rep(
  "Imputed", nrow(train[is.na(train$LotFrontage), ])
  ),
  ceiling(
  predict(frntage.rpart, train[is.na(train$LotFrontage), col.pred])
  ))))


ggplot(train.frontage, aes (x = as.numeric(as.character(V2)), colour = V1)) +
  geom_density() +
  xlab("Lot Frontage") +
  theme(legend.title = element_blank())

train$LotFrontage[is.na(train$LotFrontage)] <- ceiling(predict(frntage.rpart, train[is.na(train$LotFrontage),col.pred]))

sort(colSums(sapply(train, is.na)), decreasing = T)
```
```{r}
table(test$LotFrontage, useNA = "ifany")

# Likely predictors
col.pred <- c("MSSubClass", "MSZoning", "LotFrontage", "LotArea", "Street", "Alley", "LotShape", "LandContour", "LotConfig", "LandSlope", "BldgType", "HouseStyle", "YrSold", "SaleType", "SaleCondition")

# Predict LotFrontage
frntage.rpart <- rpart(
  LotFrontage ~ .,
  data = test[!is.na(test$LotFrontage), col.pred],
  method = "anova",
  na.action = na.omit
  )

# Let us plot the existing and imputed values and check if imputed values follow the same patten
test.frontage <-
  as.data.frame(rbind(cbind(rep(
  "Existing", nrow(test[!is.na(test$LotFrontage), ])
  ), test[!is.na(test$LotFrontage), "LotFrontage"]),
  cbind(rep(
  "Imputed", nrow(test[is.na(test$LotFrontage), ])
  ),
  ceiling(
  predict(frntage.rpart, test[is.na(test$LotFrontage), col.pred])
  ))))


ggplot(test.frontage, aes (x = as.numeric(as.character(V2)), colour = V1)) +
  geom_density() +
  xlab("Lot Frontage") +
  theme(legend.title = element_blank())

test$LotFrontage[is.na(test$LotFrontage)] <- ceiling(predict(frntage.rpart, test[is.na(test$LotFrontage),col.pred]))

sort(colSums(sapply(test, is.na)), decreasing = T)
```

```{r}
reg <- lm(SalePrice~OverallQual+GrLivArea+GarageCars+TotalBsmtSF, data = train)
summary(reg)
test$SalePrice <- predict(reg, newdata = test)
test %>%
  select(Id, SalePrice) %>%
  write.csv(file = "prediction.csv", row.names = F)
```


THIS IS WHERE I AM, REST IS RANDOM TESTING!!!




```{r}
# See all NAs
sort(colSums(sapply(train, is.na)), decreasing = T)
sort(colSums(sapply(train, is.na)), decreasing = T)
# list rows of data that have missing values 
missing <- train[!complete.cases(train),]
#head(missing)
#summary(missing)
nrow(missing)

ggplot(train, aes(x = SalePrice, fill = ..count..)) +
  geom_histogram(binwidth = 5000) +
  ggtitle("Figure 1 Histogram of SalePrice") +
  ylab("Count of houses") +
  xlab("Housing price") + 
  theme(plot.title = element_text(hjust = 0.5))

train$lSalePrice = log(train$SalePrice) #could be +1

ggplot(train, aes(x = lSalePrice, fill = ..count..)) +
  geom_histogram(binwidth = 0.05) +
  ggtitle("Figure 2 Histogram of log SalePrice") +
  ylab("Count of houses") +
  xlab("Housing Price") + 
  theme(plot.title = element_text(hjust = 0.5))

# Distribution of MSZoning
options(repr.plot.width=5, repr.plot.height=4)
ggplot(train, aes(x = MSZoning, fill = MSZoning )) + 
geom_bar()+ 
scale_fill_hue(c = 80)+
ggtitle("Figure 3 Distribution of MSZoning")+
theme(plot.title = element_text(hjust = 0.5))+
geom_text(stat='count',aes(label=..count..),vjust=-0.25)

# SalePrice vs OverallQuality
ggplot(train, aes(x = SalePrice,fill = as.factor(OverallQual))) +
  geom_histogram(position = "stack", binwidth = 10000) +
  ggtitle("Figure 6 Histogram of SalePrice") +
  ylab("Count") +
  xlab("Housing Price") + 
  scale_fill_discrete(name="OverallQual")+
  theme(plot.title = element_text(hjust = 0.5))

# convert factor to numeric
train$ExterQual2 <- as.numeric(factor(train$ExterQual, 
                                  levels = c("Ex", "Fa","Gd", "TA"),
                                  labels = c(5,2,4,3) ,ordered = TRUE))

train$ExterCond2 <- as.numeric(factor(train$ExterCond, 
                                  levels = c("Ex", "Fa","Gd", "TA","Po"),
                                  labels = c(5,2,4,3,1) ,ordered = TRUE))

train$BsmtQual2 <- as.numeric(factor(train$BsmtQual, 
                                  levels = c("Ex", "Fa","Gd", "TA"),
                                  labels = c(5,2,4,3) ,ordered = TRUE))

train$BsmtCond2 <- as.numeric(factor(train$BsmtCond, 
                                 levels = c("Fa", "Gd","Po", "TA"),
                                 labels = c(2,4,1,3) ,ordered = TRUE))

train$HeatingQC2 <- as.numeric(factor(train$HeatingQC, 
                                  levels = c("Ex", "Fa","Gd", "TA","Po"),
                                  labels = c(5,2,4,3,1) ,ordered = TRUE))
train$CentralAir2 <- as.numeric(factor(train$CentralAir, 
                                  levels = c("N", "Y"),
                                  labels = c(0,1) ,ordered = TRUE))


#select variables that be used for model buidling and heat map
model_var <- c('SalePrice', 
                'OverallQual','OverallCond','YearBuilt', 'ExterQual2','ExterCond2',
                'TotalBsmtSF','HeatingQC2', 
                'CentralAir2','GrLivArea','BedroomAbvGr','KitchenAbvGr',
                'TotRmsAbvGrd','Fireplaces',
                'GarageArea','OpenPorchSF','PoolArea',
                 'YrSold')
heat <- train[,model_var]
# HeatMap
qplot(x=Var1, y=Var2, data=melt(cor(heat, use="p")), fill=value, geom="tile") +
   scale_fill_gradient2(midpoint = 0, limit = c(-1,1), space = "Lab", 
   name="Correlation") +
   theme_minimal()+ 
   theme(axis.text.x = element_text(angle = 45, vjust = 1, size = 8, hjust = 1))+
   coord_fixed()+
   theme(plot.title = element_text(hjust = 0.4))

# Plot of high cor vals
(p1 <- ggplot(train, aes(x=GrLivArea, y=SalePrice)) + 
  geom_point(shape=1) +  
  geom_smooth(method=lm , color="red", se=FALSE)+
  ggtitle("Figure 8 Scatter plot of SalePrice and GrLivArea") +
  theme(plot.title = element_text(hjust = 0.4)))

(p2 <- ggplot(train, aes(x=TotalBsmtSF, y=SalePrice)) + 
  geom_point(shape=1) +  
  geom_smooth(method=lm , color="red", se=FALSE)+
  ggtitle("Figure 9 Scatter plot of SalePrice and TotalBsmtSF") +
  theme(plot.title = element_text(hjust = 0.4)))

(p3 <- ggplot(train, aes(x=TotRmsAbvGrd, y=SalePrice)) + 
  geom_point(shape=1) +  
  geom_smooth(method=lm , color="red", se=FALSE)+
  ggtitle("Figure 10 Scatter plot of SalePrice and TotRmsAbvGrd") +
  theme(plot.title = element_text(hjust = 0.4)))

(p4 <- ggplot(train, aes(x=GarageArea, y=SalePrice)) + 
  geom_point(shape=1) +  
  geom_smooth(method=lm , color="red", se=FALSE)+
  ggtitle("Figure 11 Scatter plot of SalePrice and GarageArea") +
  theme(plot.title = element_text(hjust = 0.4)))
```

```{r}

# Both work
sort(sapply(train[,1:80], function(x) sum(is.na(x))), decreasing = T)
sort(sapply(train, function(x) sum(is.na(x))), decreasing = T)

```


```{r}
colSums(is.na(train))
train_mean <- colMeans(train, na.rm = T)
train <- replace_na(train, replace = as.list(train_mean))
colSums(is.na(train))
```
